A Gentle Introduction and Application of Feature-Based Clustering with Psychological Time Series

### 2023-08-07 manuscript.tex
osf and github added

% Authors
\author[*,1,3]{Jannis Kreienkamp}
\author[1,3]{Maximilian Agostini}
\author[1,3]{Kai Epstude}
\author[2,3]{Rei Monden}
\author[1,3]{Peter de Jonge}
\author[1,3]{Laura F. Bringmann}
\affiliation{\hfill}

\affil[1]{University of Groningen, Department of Psychology}
\affil[2]{Hiroshima University, Graduate School of Advanced Science and Engineering}
\affil[3]{Author order TBD}

@@

We have no known conflict of interest to declare. The authors received no specific funding for this work. Materials and  software are available at \url{https://janniscodes.github.io/migration-trajectories/}  \citep{KreienkampTBD}. Materials, data, and code are available at \url{https://osf.io/TBA} \citep{KreienkampTBD}.

@@

\keywords{
    time series analysis, feature-based clustering, intensive longitudinal data, ESM\\
    \vspace{1em}
    \textit{Open Science Practices:}
    \href{https://osf.io}{\includegraphics[height=\badgeheight]{assets/open-badges-small/material-color.png}} Open Materials, 
    \href{https://osf.io}{\includegraphics[height=\badgeheight]{assets/open-badges-small/data-color.png}} Open Data,
    \href{https://osf.io}{\includegraphics[height=\badgeheight]{assets/open-badges-small/code-color.png}} Open Code, \break
    \href{https://osf.io}{\includegraphics[height=\badgeheight]{assets/open-badges-small/supplements-color.png}} Open Supplements
}

>>>>

% Authors
\author[*,1]{Jannis Kreienkamp}
\author[1]{Maximilian Agostini}
\author[1]{Kai Epstude}
\author[2]{Rei Monden}
\author[1,3]{Peter de Jonge}
\author[1,3]{Laura F. Bringmann}
\affiliation{\hfill}

\affil[1]{University of Groningen, Department of Psychology}
\affil[2]{Hiroshima University, Graduate School of Advanced Science and Engineering}
\affil[3]{ICPE}

@@

We have no known conflict of interest to declare. The authors received no specific funding for this work. Materials and  software are available at \url{https://janniscodes.github.io/migration-trajectories/} \citep{KreienkampMasked-clust-github}. Materials, data, and code are available at \url{https://osf.io/75ryj/?view_only=db14031cd8704085b5c6165c9f5ed3e4} \citep{KreienkampMasked-clust-osf}.

@@

\keywords{
    time series analysis, feature-based clustering, intensive longitudinal data, ESM\\
    \vspace{1em}
    \textit{Open Science Practices:}
    \href{https://osf.io/75ryj/?view_only=db14031cd8704085b5c6165c9f5ed3e4}{\includegraphics[height=\badgeheight]{assets/open-badges-small/material-color.png}} Open Materials, 
    \href{https://osf.io/75ryj/?view_only=db14031cd8704085b5c6165c9f5ed3e4}{\includegraphics[height=\badgeheight]{assets/open-badges-small/data-color.png}} Open Data,
    \href{https://osf.io/75ryj/?view_only=db14031cd8704085b5c6165c9f5ed3e4}{\includegraphics[height=\badgeheight]{assets/open-badges-small/code-color.png}} Open Code, \break
    \href{https://osf.io/75ryj/?view_only=db14031cd8704085b5c6165c9f5ed3e4}{\includegraphics[height=\badgeheight]{assets/open-badges-small/supplements-color.png}} Open Supplements\\
    \vspace{1em}
    Materials and software are available as part of our project GitHub repository \citep{KreienkampMasked-clust-github}. The full illustration code is also available as a tutorial-style website \citep{KreienkampMasked-illustration-github}. Materials, data, and code are available at \url{https://osf.io/75ryj/?view_only=db14031cd8704085b5c6165c9f5ed3e4} \citep{KreienkampMasked-clust-osf}.
}
